Bathtub Qualitative Reasoning

### 2016-10-21 paper.tex
paper

\section{Algorithm}
The goal of the algorithm is to construct a state graph based for a specific model and a given starting state. Constructing the state-graph is done iteratively as shown in Algorithm~\ref{alg:computing_state_graph}.

@@

In figure \ref{state-graph-base} shows all possible behaviors of the system described above. Nodes are states and each arrow represents a transition to every reachable states.

\begin{figure}\label{state-graph-base}
\centering
\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{result_base_problem.png}
\caption{Plot of the state-graph of the base problem}
\end{figure}

@@

\begin{itemize}
\item I+(Inflow, Volume): the amount of inflow increases the volume
\item I-(Outflow, Volume): the amount of outflow decreases the volume
\item P+(Volume, Height): height changes are proportional to volume changes
\item P+(Height, Pressure): pressure changes are proportional to height changes
\item P+(Pressure, Outflow): outflow changes are proportional to pressure changes
\item V(Volume(Max), Height(Max)): the height is at its highest value (Max), when the volume is at it highest value
\item V(Volume(0), Height(0)): there is no height, when there is no volume
\item V(Height(Max), Pressure(Max)): the pressure is at its highest value (Max), when the height is at it highest value
\item V(Height(0), Pressure(0)): there is no pressure, when there is no height
\item V(Pressure(Max), Outflow(Max)): the outflow is at its highest value (Max), when the pressure is at it highest value
\item V(Pressure(0), Outflow(0)): there is no outflow, when there is no pressure
\end{itemize}
\end{itemize}

\begin{figure}[H]
\centering
\includegraphics[scale=0.5]{problem_extra.eps}
\caption{Drawings of the causal model active for the extra problem}
\end{figure}

\begin{figure}\label{state-graph-extra}
	\centering
	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{result_extra_problem.png}
	\caption{Plot of the state-graph of the extra problem}
\end{figure}

>>>>

\newpage
\section{Algorithm}
The goal of the algorithm is to construct a state graph based for a specific model and a given starting state. Constructing the state-graph is done iteratively as shown in Algorithm~\ref{alg:computing_state_graph}.

@@

In figure \ref{state-graph-base} shows all possible behaviors of the system described above. Nodes are states and each arrow represents a transition to every reachable states. Nodes are labeled with the description of the current value of each quantity and its derivative.

\begin{figure}[H]\label{state-graph-base}
\centering
\includegraphics[width=\textwidth,height=7.7in,keepaspectratio]{result_base_problem.png}
\caption{Plot of the state-graph for the base problem}
\end{figure}

@@

\item \textbf{Dependencies:}
\begin{itemize}
\item I+(Inflow, Volume): the amount of inflow increases the volume
\item I-(Outflow, Volume): the amount of outflow decreases the volume
\item P+(Volume, Height): height changes are proportional to volume changes
\item P+(Height, Pressure): pressure changes are proportional to height changes
\item P+(Pressure, Outflow): outflow changes are proportional to pressure changes
\item V(Volume(Max), Height(Max)): the height is at its highest value (Max), when the volume is at it highest value
\item V(Volume(0), Height(0)): there is no height, when there is no volume
\item V(Height(Max), Pressure(Max)): the pressure is at its highest value (Max), when the height is at it highest value
\item V(Height(0), Pressure(0)): there is no pressure, when there is no height
\item V(Pressure(Max), Outflow(Max)): the outflow is at its highest value (Max), when the pressure is at it highest value
\item V(Pressure(0), Outflow(0)): there is no outflow, when there is no pressure
\end{itemize}
\end{itemize}

\begin{figure}[H]
\centering
\includegraphics[scale=0.4]{problem_extra.eps}
\caption{Drawings of the causal model active for the extra problem}
\end{figure}

\begin{figure}[H]\label{state-graph-extra}
	\centering
	\includegraphics[width=\textwidth,height=9.5in,keepaspectratio]{result_extra_problem.png}
	\caption{Plot of the state-graph for the extra problem}
\end{figure}
